Solent region: Test Maps

### 2021-07-16 Solent_Mapping_v2.Rmd
Mapping the fuel poverty for LA and LSOA added however there is a "Error: Discrete value supplied to continuous scale"

```{r Mapping the local authority energy consumption (Personal)}
# re-use the merged dataset
ggplot2::ggplot(la_merged_Transp) +
  geom_sf(aes(fill = Personal)) +
  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
```

@@

## Mapping the Indices of Multiple Deprivation

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

>>>>

```{r Mapping the local authority energy consumption (Personal)}
# re-use the merged dataset
ggplot2::ggplot(la_merged_Transp) +
  geom_sf(aes(fill = Personal)) +
  scale_fill_gradient(name = "Personal: Thousand tonnes of oil equivalent (ktoe)", low="green",high="red") 
```
## Mapping Fuel Poverty 
###2021 Proportion of Population
```{r Loading in the 2021 Local Authority Fuel Poverty Data}
inFile<-paste0(dataFolder, "Fuel Poverty/2021 LA_Fuel_Poverty.csv")
la_fuelpov_2021<-readr::read_csv(inFile)
head(la_fuelpov_2021)
```
```{r Mapping Local Authority Fuel Poverty 2021}
la_fuelpov_2021$lad18cd <- la_Transport$"Area Codes" # Creating a variable with the local authority code in the same name 
la_merged_Fuelpov2021 <- merge(la_sf_data, la_fuelpov_2021)# Merge the local Authority boundaries and the Fuel Poverty data
ggplot2::ggplot(la_merged_Fuelpov2021) +
  geom_sf(aes(fill = "Proportion of households fuel poor (%)")) +
  scale_fill_gradient(name = "Proportion of households fuel poor (%)", low="green",high="red")
```

@@

### Mapping the Indices of Multiple Deprivation

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
###Mapping Fuel Poverty
####2021 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2021<-readr::read_csv (inFile)
head(lsoa_fuelpov_2021)
```
```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
  geom_sf(aes(fill="Proportion of households fuel poor (%)"))+ # which data set has the scores?
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
```
